IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-11 main.tex
:pencil: Update manuscript

\interdisplaylinepenalty=2500
\pgfplotsset{compat=newest}
\usetikzlibrary{plotmarks}
\usetikzlibrary{arrows.meta}
\usepgfplotslibrary{patchplots}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}
\usetikzlibrary{arrows,matrix,positioning}

@@

            The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. \cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS). Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the RF-to-DC conversion efficiency of rectifiers depends on the input power and waveform shape. It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, and performed joint waveform and beamforming design for WPT. Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}. A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage is then demonstrated in a prototype with channel acquisition \cite{Kim2017}. Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region; 3) a combination of PS and TS is generally the best strategy; 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG); 5) modeling rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answer sheds new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
		\end{subsection}

@@

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation. \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}. In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift for practical IRS. To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}. The hardware architecture, design challenges and application opportunities of practical IRS are covered in \cite{Wu2020}. In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
		\end{subsection}

		\begin{subsection}{IRS-Aided SWIPT}
			By integrating IRS with SWIPT, its smart and effective reflection can enhance the R-E tradeoff and improve the end-to-end power efficiency. For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}. It was also claimed that Line-of-Sight (LoS) links could boost the WSP since rank-deficient channels require fewer energy beams \cite{Wu2020a}. However, \cite{Wu2020b,Tang2019,Wu2020a} were based on an inaccurate linear energy harvester model that is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}. Based on practical IRS and energy harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization is divided into a reflection mode design stage and a joint reflection mode selection and precoder design stage. The proposed framework provides a flexible balance between performance and complexity. To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network. In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with practical co-located information decoder and energy harvester. We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.

			\emph{First,} we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model in \cite{Clerckx2016a}. Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function. To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the TS and PS receiving modes. The proposed joint waveform, active and passive beamforming architecture exploits across frequency and spatial domains the rectifier nonlinearity, the channel selectivity, and a beamforming gain to enlarge the achievable R-E region. This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.

			\emph{Second,} we characterize each R-E boundary point by energy maximization under rate constraint, and solve the problem by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT). For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) even with rectifier nonlinearity. For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and retrieve the IRS phase shift by eigen decomposition with optimality proof. Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique. The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence. This is the first paper to jointly optimize waveform and active/passive beamforming in IRS-aided SWIPT.

			\emph{Third,} we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm. The Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in the time and power domains to facilitate practical SWIPT implementation. Some modifications are then made on the passive beamforming design to accommodate the low-complexity waveform schemes. In this case, the R-E region is obtained by varying the duration ratio under the TS mode and varying the combining and splitting ratios under the PS mode. The proposed low-complexity BCD algorithm achieves a good balance between performance and complexity.

			\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms. It is concluded that 1) IRS not only enhances the equivalent channel but also enables flexible subchannel design in the frequency domain, which is essential for SWIPT; 2) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 6) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 7) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 8) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 9) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.

@@

			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters. $j$ denotes the imaginary unit. $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix. $\boldsymbol{I}$ denotes the identity matrix. $\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the subspace spanned by real nonnegative and complex $x \times y$ matrices. $\Re\{\cdot\}$ retrieves the real part of a complex entity. $[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector. $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm. $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix. $\odot$ denotes the Hadamard product. $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite. $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal. $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity). The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$. $\sim$ means ``distributed as''. $(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterated value and the stationary solution.
		\end{subsection}
	\end{section}

	\begin{section}{System Model}\label{se:system_model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{system.pdf_tex}
			\caption{An IRS-aided multi-carrier SWIPT system.}
			\label{fi:system}
		\end{figure}

		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where an $M$-antenna AP delivers information and power simultaneously, through an $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands. We consider the quasi-static block fading model and assume the CSIT of direct and cascaded channels is known. The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.

		\begin{subsection}{Transmitted Signal}
			Following \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated waveform (deterministic multisine) to boost the spectrum and energy efficiency. The information signal transmitted over subband $n \in \{1, \dots, N\}$ at time $t$ is
			\begin{equation}
				\boldsymbol{x}_{\mathrm{I},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
			\end{equation}
			where $\boldsymbol{w}_{\mathrm{I},n} \in \mathbb{C}^{M \times 1}$ is the information precoder at subband $n$, $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ is the information symbol at subband $n$, and $f_n$ is the frequency of subband $n$. On the other hand, the power signal transmitted over subband $n$ at time $t$ is
			\begin{equation}
				\boldsymbol{x}_{\mathrm{P},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
			\end{equation}
			where $\boldsymbol{w}_{\mathrm{P},n} \in \mathbb{C}^{M \times 1}$ is the power precoder at subband $n$. Therefore, the superposed signal transmitted over all subbands at time $t$ is
			\begin{equation}
				\boldsymbol{x}(t) = \Re{\left\{\sum_{n=1}^N(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
			\end{equation}
			We also define $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$.
		\end{subsection}

		\begin{subsection}{Reflection Pattern and Composite Channel}
			According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component. The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedance. IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and the reflection coefficient is defined as
			\begin{equation}
				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l},
			\end{equation}
			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the IRS, in practice $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$. This paper sticks to the most common IRS model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.} and $\theta_l \in [0,2\pi)$ is the phase shift. We also define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS vector and matrix, respectively.\footnote{Note that $\boldsymbol{\phi}=\mathrm{diag}(\boldsymbol{\Phi}^*)$ by definition.}

@@

			\begin{remark}\label{re:subband_tradeoff}
				The cascaded channel varies at different subbands but the reflection cannot be designed independently at different frequencies. Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite channel should be tuned adaptively to meet the specific requirement of multi-carrier SWIPT. For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$). That is to say, IRS essentially enables an flexible subchannel design. In the MISO case, a similar effect also exists in the spatial domain. Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
			\end{remark}
		\end{subsection}

>>>>

\interdisplaylinepenalty=2500
\pgfplotsset{compat=newest}
\usetikzlibrary{plotmarks}
\usetikzlibrary{arrows.meta}
\usepgfplotslibrary{patchplots}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}
\DeclareSIUnit{\belA}{BA}
\DeclareSIUnit{\dBA}{\deci\belA}
\usetikzlibrary{arrows,matrix,positioning}

@@

            The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. \cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS). Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the RF-to-DC conversion efficiency of rectifiers depends on the input power and waveform shape. It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, and performed joint waveform and beamforming design for WPT. Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}. A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage was then demonstrated in a prototype with channel acquisition \cite{Kim2017}. Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region; 3) a combination of PS and TS is generally the best strategy; 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG); 5) modeling rectifier nonlinearity is beneficial to system performance and essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answers shed new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
		\end{subsection}

@@

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation. \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}. In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice. To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}. The hardware architecture, design challenges, and application opportunities of practical IRS were covered in \cite{Wu2020}. In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time video transmission at \si{GHz} and mmWave frequency.
		\end{subsection}

		\begin{subsection}{IRS-Aided SWIPT}
			By integrating IRS with SWIPT, the constructive reflection can boost the end-to-end power efficiency and improve the R-E tradeoff. In multi-user cases, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}. It was also claimed that Line-of-Sight (LoS) links could boost the WSP since rank-deficient channels require fewer energy beams \cite{Wu2020a}. However, \cite{Wu2020b,Tang2019,Wu2020a} were based on a linear energy harvester model that is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}. Based on practical IRS and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage. The proposed framework provides a flexible tradeoff between performance and complexity. To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network. In this paper, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with co-located information decoder and energy harvester. We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.

			\emph{First,} we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \cite{Clerckx2016a}. Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function. To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the TS and PS receiving modes. The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable R-E region. This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.

			\emph{Second,} we characterize each R-E boundary point by energy maximization under a rate constraint. The problem is solved by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT). For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) even with rectifier nonlinearity. For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and retrieve the IRS phase shift by eigen decomposition with optimality proof. Finally, the superposed waveform and the splitting ratio are optimized by the Geometric Programming (GP) technique. The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence. This is the first paper to jointly optimize waveform and active/passive beamforming in IRS-aided SWIPT.

			\emph{Third,} we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm. To facilitate practical SWIPT implementation, the Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in time and power domains, respectively. The passive beamforming design is also adapted to accommodate the low-complexity waveform schemes. The proposed low-complexity BCD algorithm achieves a good balance between performance and complexity.

			\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms. It is concluded that 1) IRS not only provides constructive reflection but also enables flexible subchannel design in the frequency domain, which is essential for SWIPT; 2) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 6) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 7) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 8) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 9) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.

@@

			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters. $j$ denotes the imaginary unit. $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix. $\boldsymbol{I}$ denotes the identity matrix. $\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the space of real nonnegative and complex $x \times y$ matrices. $\Re\{\cdot\}$ retrieves the real part of a complex entity. $[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector. $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm. $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix. $\odot$ denotes the Hadamard product. $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite. $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal. $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity). The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$. $\sim$ means ``distributed as''. $(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterated value and the stationary solution.
		\end{subsection}
	\end{section}

	\begin{section}{System Model}\label{se:system_model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{system.pdf_tex}
			\caption{An IRS-aided multi-carrier MISO SWIPT system.}
			\label{fi:system}
		\end{figure}

		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where an $M$-antenna AP delivers information and power simultaneously, through an $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands. We consider a quasi-static block fading model and assume the CSIT of direct and cascaded channels is known. The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.

		\begin{subsection}{Transmitted Signal}
			Following \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated deterministic multisine to boost the spectrum and energy efficiency. The information signal transmitted over subband $n \in \{1, \dots, N\}$ at time $t$ is
			\begin{equation}
				\boldsymbol{x}_{\mathrm{I},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
			\end{equation}
			where $\boldsymbol{w}_{\mathrm{I},n} \in \mathbb{C}^{M \times 1}$ is the information precoder at subband $n$, $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ is the information symbol at subband $n$, and $f_n$ is the frequency of subband $n$. On the other hand, the power signal transmitted over subband $n$ at time $t$ is
			\begin{equation}
				\boldsymbol{x}_{\mathrm{P},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
			\end{equation}
			where $\boldsymbol{w}_{\mathrm{P},n} \in \mathbb{C}^{M \times 1}$ is the power precoder at subband $n$. Therefore, the superposed signal transmitted over all subbands at time $t$ is
			\begin{equation}
				\boldsymbol{x}(t) = \Re{\left\{\sum_{n=1}^N(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
			\end{equation}
			We also define $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$.
		\end{subsection}

		\begin{subsection}{Reflection Pattern and Composite Channel}
			According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component. The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedance. IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and the reflection coefficient is defined as
			\begin{equation}
				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l},
			\end{equation}
			where $Z_0$ is the real-valued characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the IRS, $R_l > 0$ in practice such that $\eta_l < 1$ and is a function of $\theta_l$. This paper sticks to the most common IRS model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.} and $\theta_l \in [0,2\pi)$ is the phase shift. We also define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L)=\mathrm{diag}(\boldsymbol{\Phi}^*) \in \mathbb{C}^{L \times L}$ as the IRS vector and matrix, respectively.

@@

			\begin{remark}\label{re:subband_tradeoff}
				The cascaded channel varies at different subbands, but the reflection cannot be designed independently at different frequencies. Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite subchannels should be tuned adaptively to meet the specific requirement of multi-carrier SWIPT. For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$). That is to say, IRS essentially enables a flexible subchannel design. In the MISO case, a similar effect also exists in the spatial domain. Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
			\end{remark}
		\end{subsection}

		\begin{subsection}{Received Signal}
			The received superposed signal at the single-antenna UE is\footnote{We assume that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
			\begin{equation}
				y(t) = \Re\left\{\sum_{n=1}^N{\Bigl(\boldsymbol{h}_{n}^H}{(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n})+\tilde{n}_n(t)\Bigr)}{e^{j2{\pi}{f_n}{t}}}\right\},
			\end{equation}
			where $\tilde{n}_n(t)$ is the noise at RF band $n$. Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for information decoding.
		\end{subsection}
